Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays

### 2019-04-09 reports/paper1/paper.tex
Revision

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves calculations on acquisition of hundreds of angles of the sample.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $256\times 256$ image. Note the y-axis change scale.}
  \label{fig:inference_timing}
\end{figure*}

>>>>

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves calculations on acquisition of hundreds of angles of the sample.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $256\times 256$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note the y-axis change scale.}
  \label{fig:inference_timing}
\end{figure*}
